\chapter{Summary}

In this report we describe the activities performed and milestones met for the
following SensorLab seed grants:

\begin{enumerate}
    \item Automated real-time detection of closed-loop communication in spoken
        dialogue.
    \item Development of an open-source dashboard for team communication
        experiments.
\end{enumerate}

The projects were designed to be complementary to each other, and intended to
enable studies of real-time spoken team communication in ambulatory settings.

The scope of our proposed tasks was ambitious, and we were unfortunately not
able to finish the development of the wearable audio streaming device (WASD)
\autoref{sec:wasd}.  However, we are happy to report that we were able to (i)
develop and evaluate a rule-based closed-loop communication detection algorithm
(\autoref{sec:clc}) and (ii) develop a prototype of the proposed dashboard for
visualizing and controlling team communication experiments
(\autoref{ch:dashboard}).

In order to develop a competitive external NSF grant proposal involving the
SensorLab, further work needs to be done to complete the development of the
WASD. We plan to continue working with the Raspberry Pi devices purchased with
this seed grant in order to finish developing and testing the audio streaming
pipeline.

Simultaneously, we will improve our closed-loop communication detection system,
exploring both refining the existing rule-based system, as well as a machine
learning approach.

Once pilot data collection starts in earnest, the dashboard will prove a
valuable tool for experiment control, visualization, and troubleshooting.

The project has contributed to training and skill development for 3
undergraduates, 3 master's students, and a research programmer.
